A 38 Million Year Old Neptune-Sized Planet in the Kepler Field

### 2021-12-06 paper_review/response_1.txt

REVIEWER COMMENT
----------
Line 78 (Kepler ages): Consider adding citation to Walkowicz & Basri
(2013)

RESPONSE
----------
> Done, thank you.

REVIEWER COMMENT
----------
Line 93: Clarify origin of name delta Lyr, given there are two
pre-existing names, and how they overlap. It might also be worth
mentioning Kerr's Cep-Her association as in prep just to save future
readers the headache of cross-identifying them, either here or in Sec
2.1

RESPONSE
----------
> delta Lyra cluster was the first name suggested by Stephenson
> (1958), and it is the default name listed in SIMBAD.  It was also
> the name used in the title of Eggen's 1967 paper.
>
> The cluster was called Stephenson-1 by people other than
> Stephenson, including by Kounkel & Covey 2019.  The Kounkel & Covey
> 2019 "Theia" catalog identifiers are simply given to any cluster in
> their catalog, in addition to any previous names that existed.
>
> The overlap between the earlier lists (Stephenson 1958, Eggen 1968,
> Kharchenko et al. 2012) and the Theia 73 list from Kounkel & Covey
> 2019 is only present in the stars closest to delta Lyr itself.  For
> instance, see the 30 stars shown in Figure 1 of Eggen 1968.  The
> broader "complex" shown in Figure 1 of our manuscript was to our
> knowledge first reported to be a set of kinematically associated
> stars by Kounkel & Covey -- inasmuch as an "HDBScan group" implies
> kinematic association.
>
> Regarding Ronan Kerr's view of the delta Lyr cluster as a component
> of the larger Cep-Her complex, we would prefer to leave this as
> Ronan's result to present.  There's significant work here in
> designing the clustering method and verifying that it works.
> There's also work in understanding the overall structure of the
> broader association (which is different in nuanced ways from the
> gray Theia 73 points in Figure 1).  Given these complications, and
> the potential importance of the complex given its proximity and
> age, we really would prefer to leave this for the in prep R. Kerr
> work.  And similarly, the introduction of the term "Cep-Her
> complex" is probably best left for that future work, where it can
> be mentioned that the "del Lyr cluster" is a subset of this
> complex.

@@

REVIEWER COMMENT
----------
Fig 3: It may be helpful to include one of the even younger clusters
on the CMD (i.e. to bracket delta Lyra), though perhaps it makes the
plot too busy.

RESPONSE
----------
> Please see camd_with_UCL.png attached.  This does make the plot a
> bit too busy, in our opinion.

REVIEWER COMMENT
----------
Page 3: Consider re-organizing. Based on the 1st paragraph, I thought
the quantitative analysis would only deal with Pleiades and IC 2602
and one might infer reddening was only calculated for these clusters
(whereas I assume the latter are also corrected for reddening prior
to the analysis described). My suggestion would be to introduce all
the clusters first. It would also be helpful to list the age of IC
2602 at some point in the text.

RESPONSE
----------
> Thank you for this suggestion.  The first paragraph of Section
> 2.2.1 has been reorganized to now introduce all five of the
> relevant clusters: UCL, IC 2602, del Lyr cluster, mu-Tau, and the
> Pleaides.  The second paragraph has been modified to account for
> this change.  The extinction for UCL is now also listed in the
> text.  So is the adopted age of IC 2602.

@@

REVIEWER COMMENT
----------
Line 391: It would be helpful to state the star's RUWE in the text here.
Additionally, I believe RUWE acornym was already defined previously.

RESPONSE
----------
> Done, thank you.

REVIEWER COMMENT
----------
Section 3.2: Comment on whether the binary companion should effect
the rotation measurement of the host star (either here, or in the
rotation section).

RESPONSE
----------
> We've added the following sentence at the beginning of Section 4.1,
> when the Kepler light curve is introduced
>
> """
> The resulting photometry is dominated by a quasi-periodic starspot
> signal with a peak-to-peak amplitude that varies between 2\% and
> 8\%.  \added{Given that the secondary companion's brightness in the
> Kepler band is 1\% to 2\% that of the primary, source confusion for
> the rotation signal is not expected to be an issue.}
> """
>
> The rationale is that the rotation amplitude on the secondary would
> need to be a factor of >two times its intrinsic brightness for any
> confusion to happen, and the primary would need to not show any
> rotation signal.  Such large variability amplitudes have not been
> observed except for disked stars (e.g., Rebull+2020, Figure 10),
> and there is no evidence for a secondary period in the Lomb Scargle
> periodograms.

@@

REVIEWER COMMENT
----------
One note about the transit analysis: The MuSCAT3 data was introduced
as supporting evidence but the conclusion (that the transits appear
achromatic) was never explicitly stated.

RESPONSE
----------
> Thank you -- we have reworded this section to improve the clarity
> with which this point is made.

@@

REVIEWER COMMENT
----------
Lines 142-144: perhaps rephrasing this would clarify that the authors
did not use Kepler-1627 as a fiducial star about which to select
cluster members, and that they restricted the analysis to one of
several sub-clusters or clumps which contained Kepler-1627.

RESPONSE
----------
> We have rephrased Lines 142-144 to clarify the meaning, which is
> indeed what the reviewer has stated.

REVIEWER COMMENT
----------
Figure 1: the first three panels would be more effective if they were
plotted at the same scale and with appropriately aligned axes. As
such the upper right panels are too small to be useful. Consider
leaving out the Sun (which is irrelevant) so as to have a more
appropriate choice of scale to how the details of the cluster. The
purpose of the fourth panel (tangential velocities) and the second
line in the caption are unclear to me. Aren't the tangential
velocities known from Gaia proper motions and parallaxes? Why
calculate them with the assumption of common space motion? If that is
done, what does it show, anyway?

RESPONSE
----------
> Thank you for these important points of feedback.
>
> The Sun has been included to clarify the direction along which
> parallax uncertainties are expected to produce erroneous
> clusterings (analogous to the "Fingers of God" effect in the
> extragalactic literature).  This is relevant because the HDBScan
> clustering method used by Kounkel & Covey in their 2019 paper
> likely was susceptible to this systematic effect.  A sentence has
> been added to the caption of Figure 1 to clarify this point.
> 
> The {X,Y}, {Z,X}, and {Z,Y} panels are plotted at different scales
> in order to keep the aspect ratios roughly correct.  The reported
> KC2019 cluster members span {ΔX, ΔY, ΔZ} of roughly {400, 600, 200}
> parsecs,  which grows to ~{600, 600, 200} parsecs when including
> the Sun.  The {Z,X} and {Z,Y} panels should therefore roughly have
> aspect ratios of 1:3 in order for the parsec to not be stretched
> too much in either dimension.  The top-down {X,Y} view is the most
> informative dimension, which is why it is enlarged related to the
> edge-on views (and its 1:1 aspect ratio is set by the same
> consideration).
>
> Finally, the tangential velocities are important because they tell
> us whether the structures are kinematically coherent.  Open
> clusters typically have velocity dispersions of order ~1km/s.
> Meingast et al. 2021 (A&A 645 84) for instance suggest tangential
> velocities <2 km/s (from the mean cluster velocity) as a plausible
> cutoff for selecting candidate cluster members.  One needs to
> compute these as relative tangential velocities instead of just
> looking at the proper motions because the proper motions are
> changed by line-of-sight projection effects, especially when the
> clusters appear stretched over tens of degrees on-sky.  See for
> instance Figure 2 of Meingast+2021, or Figure 14 of Bouma+2021 (AJ,
> 162, 197).  In our case, the tangential velocities indicate that
> the spread in Kounkel & Covey 2019's reported cluster members is
> ~10km/s, which is large enough that it does not make obvious
> kinematic sense to consider all of these stars to be part of the
> same structure.
>
> We've added a few sentences in the manuscript to clarify these
> points.

@@

RESPONSE
----------
> Done, thank you.

REVIEWER COMMENT
----------
Section 4.1.3 and Figure 6

The significance of this slope is unclear and a sigma is not a good
way to evaluate it. Perform a ratio of chi-squared or F-test to
evaluate it vs. a flat line.

RESPONSE
----------
> The second paragraph of Section 4.1.3 has been modified to mention
> the difference in BIC, and the corresponding approximate Bayes
> factor. 
>
> The slope of $-21 \pm 10\,{\rm min\,day}^{-1}$ is similar to that
> found by \citet{holczer_time_2015}. \added{The $\chi^2$ of the
> best-fit line is $306.1$, with $n=140$ data points.  An alternative
> model of a flat line yields $chi^2=315.6$.  The difference in the
> Bayesian information criterion (BIC) between the two models is
> ${\rm BIC}_{\rm flat} - {\rm BIC}_{\rm line} = 4.5$, which
> corresponds to a Bayes factor of $\approx$9.4. According to the
> usual \citet{kass_bayes_1995} criteria, this is ``positive''
> evidence for the model with a finite slope.  We view it as
> suggestive evidence at best, particularly given the excess scatter
> in the transit timing measurement uncertainties.}
>
> We have also modified the caption of Figure 6 to clarify that this
> is not a detection.

@@

REVIEWER COMMENT
----------
Lines 613-614: it would be good to quantify this, i.e. how faint an
unresolved companion or background star must be based on the star's
position in the CMD.

RESPONSE
----------
> Visually, one can see that the width of the single-star sequence of
> δ Lyr candidates (black points) in the upper-right panel of Figure
> 3 is <~0.2 mag.  So, if we saw a star with the same (BP-RP) color
> as Kepler 1627 that were more than ~0.3 mag brighter in M_G, we
> would classify it as a likely photometric binary.  This means we
> are able to exclude stars ~0.32* as bright as the primary (in Gaia
> G-band). This corresponds to excluding bound companions more
> massive than ~0.85 Msun (the primary's mass is ~0.95 Msun).  The
> SB2 tests do much better if the velocity separation exceeds the CCF
> width (down to 1% as bright as the primary;
> https://ui.adsabs.harvard.edu/abs/2015AJ....149...18K/abstract).
> For brevity, we would prefer to not present this information in the
> text.

@@

RESPONSE
----------
> Thank you for this point; we've updated the text to say
> "signal-to-noise" rather than "precision".

REVIEWER COMMENT
----------
line 678-683: The Ca II HK activity indicator "S" as well as the
H-alpha equivalent width could be obtained from the HIRES spectrum.
Have the authors checked fora X-ray or UV (Galex) detection of this
star? The star is likely not detected but its worth a look. In the
same vein, the authors may wish to comment on whether the star's
infrared emission indicates or rule out a substantial debris disk --
the star is detected in WISE (and perhaps Spitzer?)

RESPONSE
----------

> Regarding the S-values, they are shown in the second panel of
> Figure 7, and are also reported in Table 6.  The line profile
> changes shown in Figure 12 suggested that the majority of the RV
> variation observed was due to starspot-induced variations.
> Quantitative measurements of the H-alpha EWs are not expected to
> change this picture, and so we opt to not include them.
>
> Regarding the NIR, UV, and X-ray detections, we searched Vizier
> within a radius of 4 arcseconds.
>
> For the X-ray (i.e., ROSAT), there were no reported detections in
> Vizier.
>
> For the NIR and the possibility of a debris disk, Kepler-1627 is
> detected in W1, W2, W3, and W4 (see
> kepler1627_vizier_photometry.png attached).  While W4 might be in
> excess of the usual Rayleigh-Jeans tail, and this could be
> quantified by fitting synthetic stellar atmospheres, this type of
> analysis is best done at the population level, particularly given
> the calibration uncertainties that are present in W4 (e.g., Cotten
> & Song 2016, ApJS 225 15).  Since Kepler-1627 has not been
> identified as even a candidate debris disk host in the previous
> literature that performs these population-level infrared excess
> analyses, we opt to not speculate on this topic.
>
> For the UV, Olmedo+2015 reported a coincident source with NUVmag of
> 19.052 +/- 0.017 [AB mags], with a NUV S/N of 65 (2015, ApJ, 813,
> 100), through the GALEX-CAUSE Kepler survey.  UV detections can
> sometimes be used as a youth indicator (e.g., Figure 9 of
> Newton+2021 AJ 161 65, which Newton et al attribute from the idea
> in Shkolnik+2011, ApJ 727 6).  For Kepler-1627, we have 2MASS J =
> 11.690+/-0.021, and therefore m_NUV-m_J = 7.36.  Given the Gaia
> (BP-RP)0 of 0.977, comparing to Figure 9 of Newton+2021 we find
> that Kepler-1627 overlaps with late-G type stars in Psc-Eri, the
> Pleiades, and the Hyades.  In other words, the UV flux is not a
> particularly strong diagnostic of the age for Kepler-1627 as an
> individual star.  
>
> To substantiate the latter claim, we cross-matched our lists of
> IC2602, Pleaides, and δ Lyr cluster members against 2MASS and
> GALEX.  The results are in galex_jmk.png and galex_bpmrp.png,
> attached.  IC2602 only got a few matches because it was in a region
> of sky not observed by GALEX.  We see that the earliest A and F
> stars in the del Lyr cluster (38 Myr) are brighter in the UV than
> the Pleiades sequence (112 Myr).  However, there's not really any
> new information in this statement that goes beyond the work that's
> already been done in the manuscript using Gaia isochrones and the
> stellar rotation.  So, for brevity, we would prefer to omit
> this analysis from the manuscript -- but thank you for suggesting
> it!

### 2021-12-06 paper/ms.tex
update response (ready to resubmit)

For instance, the ``mini-Neptunes'', thought to be made of metal
cores, silicate mantles \citep{kite_atmosphere_2020}, and extended
hydrogen-dominated atmospheres, are expected to shrink
in size by factors of several over their first $10^8$ years.
Specifically, in the models of \citet{owen_atmospheres_2016} and
\citet{owen_constraining_2020}, the $\approx$$5\,M_\oplus$ planets start
with sizes of 4\,--\,12\,$R_\oplus$ shortly after the time of disk
dispersal ($\lesssim$$10^7$\,years), and shrink to sizes of
2\,--\,4\,$R_\oplus$ by 10$^8$ years.  While the majority of this change
is expected to occur within the first few million years after the disk
disperses \citep{ikoma_situ_2012}, stellar
irradiation and internal heat can also power gradual outflows
which, if strong enough, can deplete or entirely strip the atmosphere \citep{lopez_how_2012,Owen_Wu_2013,ginzburg_corepowered_2018}.\added{ The latter photoevaporative and core-powered
	outflows are thought to persist for $\approx$$10^8$ to $\approx$$10^9$ years,
	though the details depend on the planetary masses,
	the irradiation environments, and the initial atmospheric
	mass fractions \citep{owen_evaporation_2017,gupta_signatures_2020,2021MNRAS.503.1526R,2021MNRAS.501L..28K}.} Discovering young planets, measuring their masses, and detecting their
atmospheric outflows are key steps toward testing this paradigm, which
is often invoked to explain the observed radius distribution of mature
exoplanets \citep{Fulton_et_al_2017,van_eylen_asteroseismic_2018}.

@@

We measured the isochrone age using an empirical approach.  The \added{upper }left
panel of Figure~\ref{fig:age} shows the color-absolute magnitude
diagram (CAMD) of candidate \cn\ members, IC\,2602\added{ ($\approx 38$\,Myr)}, the Pleiades\added{ ($\approx 115$\,Myr)}, and
the field. The stars from the Pleiades and IC\,2602 were adopted from
\citet{CantatGaudin2018a}, and the field stars are from the Gaia EDR3
Catalog of Nearby Stars \citep{gaia_gcns_2021}.  
\added{We also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}).
We adopted the UCL members from \citet{Damiani2019}.
For visual clarity, the latter two clusters are not shown in Figure~\ref{fig:age}.
}
We cleaned \replaced{these}{the membership lists}
following the data filtering criteria from \citet[][Appendix
B]{GaiaCollaboration2018}, except that we weakened the parallax
precision requirement to $\varpi/\sigma_\varpi>5$.  \added{This also involved cuts
on the photometric signal to noise ratio, the number of visibility
periods used, the astrometric $\chi^2$ of the single-source solution, and the
$G_{\rm BP}-G_{\rm RP}$ color excess factor.} These filters were
designed to include genuine binaries while omitting instrumental
artifacts.

@@

Of the \noriginal\ candidate \cn\ members reported by
\citet{KounkelCovey2019}, \nwithtess\ stars were amenable to rotation
period measurements ($G<17$ and $\bpmrpo>0.5$) using the TESS full
frame image data. 
\added{As a matter of
scope, we restricted our attention to the \nkinwithtess\ stars
discussed in Section~\ref{sec:kinematicselection} in the spatial and
kinematic proximity of Kepler\,1627. }
We extracted light curves from
the TESS images using the nearest pixel to each star, and regressed
them against systematics with the causal pixel model implemented in
the \texttt{unpopular} package \citep{hattorio_2021_cpm}.  We then
measured candidate rotation periods using a Lomb-Scargle periodogram
\citep{lomb_1976,scargle_studies_1982,astropy_2018}.  To enable cuts
on crowding, we queried the Gaia source catalog for stars within a
$21\farcs0$ radius of the target star (a radius of 1 TESS pixel).
Within this radius, we recorded the number of stars with greater
brightness than the target star, and with brightness within 1.25 TESS magnitudes of the target star.

@@

We therefore isolated each of the 144 observed transits to within
$\pm4.5$\,hr of each transit, and fitted each window with both {\it
i)} a local \added{second or fourth-order }polynomial baseline plus the transit, and {\it ii)} a local linear
trend\added{ plus the transit}.  \deleted{We considered the results both for a second and fourth-order
time-dependence in the local baseline.  }We let the mid-time of each
transit float, and then calculated the residual between the measured
mid-time and that of a periodic orbit.  This residual, the transit
timing variation, is plotted in Figure~\ref{fig:corr} against
the local linear slope for the fourth-order polynomial baseline.  The
slope of $-21 \pm 10\,{\rm min\,day}^{-1}$ is similar to that
found by \citet{holczer_time_2015}. \added{The
best-fit line yields $\chi^2 = 306.1$, with $n=140$ data points.  An alternative
model of just a flat line yields $\chi^2=315.6$.  The difference in the
Bayesian information criterion between the two models is ${\rm
BIC}_{\rm flat} - {\rm BIC}_{\rm line} = 4.5$,
which corresponds to a Bayes factor of $\approx$9.4. According to the
usual \citet{kass_bayes_1995} criteria, this is ``positive'' evidence
for the model with a finite slope.  We view it as suggestive evidence
at best, particularly given the excess scatter in the transit timing
measurement uncertainties.}

@@

In the context of the transiting planet population, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages include K2-33
\citep{Mann_K2_33b_2016,David_et_al_2017}, DS~Tuc
\citep{benatti_possibly_2019,newton_tess_2019}, HIP~67522
\citep{rizzuto_tess_2020}, TOI~837 \citep{bouma_cluster_2020}, the
two-planet AU~Mic \citep{plavchan_planet_2020,martioli_aumicbc_2021}
and the four-planet V1298~Tau \citep{david_four_2019}.  \pn\ is one of
the smaller planets in this sample ($3.82\pm0.16\,R_\oplus$), which
could be linked to the selection effects imposed by spot-induced
photometric variability at very young ages \citep[{\it
e.g.},][]{zhou_2021_tois}.  \replaced{However,}{However, it seems that} smaller planets could have been
detected: \added{based on the per-target detection contours, }the Kepler pipeline's median completeness extended to
$1.6\,R_\oplus$ at 10~day orbital periods, and $3.3\,R_\oplus$ at
100~days
\citep{2021ascl.soft07027B}.
\added{These limits account for the spot-induced variability in the
system through
a correction based on the Combined Differential Photometric Precision
(CDPP) in the \sn\ light curve over the relevant transit timescales
\citep{2017ksci.rept...19B}.} The large size of \pn\ relative
to most Kepler mini-Neptunes might therefore support a picture
in which the typical $5\,M_\oplus$ \deleted{to 10$\,M_\oplus$} mini-Neptune
\citep{wu_mass_2019} loses a significant fraction of its primordial
atmosphere over its first gigayear
\citep{Owen_Wu_2013,ginzburg_corepowered_2018}.  
\added{
It could also be consistent with a scenario in which an earlier ``boil-off'' of
the planet's atmosphere during disk dispersal decreases the entropy of
the planetary interior, leading to a $\sim$10$^8$ year Kelvin-Helmholtz cooling and
contraction timescale
\citep{owen_constraining_2020}.
Confirming either of these scenarios would require a measurement
of the planetary mass; otherwise, alternative explanations for its large size
also include that it is abnormally massive, or that it has an abnormally
large envelope to core mass ratio.}

>>>>

For instance, the ``mini-Neptunes'', thought to be made of metal
cores, silicate mantles \citep{kite_atmosphere_2020}, and extended
hydrogen-dominated atmospheres, are expected to shrink
in size by factors of several over their first $10^8$ years.
Specifically, in the models of \citet{owen_atmospheres_2016} and
\citet{owen_constraining_2020}, the $\approx$$5\,M_\oplus$ planets start
with sizes of 4\,--\,12\,$R_\oplus$ shortly after the time of disk
dispersal ($\lesssim$$10^7$\,years), and shrink to sizes of
2\,--\,4\,$R_\oplus$ by 10$^8$ years.  While the majority of this change
is expected to occur within the first few million years after the disk
disperses \citep{ikoma_situ_2012}, stellar
irradiation and internal heat can also power gradual outflows
which, if strong enough, can deplete or entirely strip the atmosphere \citep{lopez_how_2012,Owen_Wu_2013,ginzburg_corepowered_2018}.\added{ The photoevaporative and core-powered
	outflows are thought to persist for $\approx$$10^8$ to $\approx$$10^9$ years,
	though the details depend on the planetary masses,
	the irradiation environments, and the initial atmospheric
	mass fractions \citep{owen_evaporation_2017,gupta_signatures_2020,2021MNRAS.503.1526R,2021MNRAS.501L..28K}.} Discovering young planets, measuring their masses, and detecting their
atmospheric outflows are key steps toward testing this paradigm, which
is often invoked to explain the observed radius distribution of mature
exoplanets \citep{Fulton_et_al_2017,van_eylen_asteroseismic_2018}.

@@

We measured the isochrone age using an empirical approach.  The \added{upper }left
panel of Figure~\ref{fig:age} shows the color-absolute magnitude
diagram (CAMD) of candidate \cn\ members, IC\,2602\added{ ($\approx 38$\,Myr)}, the Pleiades\added{ ($\approx 115$\,Myr)}, and
the field. The stars from the Pleiades and IC\,2602 were adopted from
\citet{CantatGaudin2018a}, and the field stars are from the Gaia EDR3
Catalog of Nearby Stars \citep{gaia_gcns_2021}.\added{ We also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}).
We adopted the UCL members from \citet{Damiani2019}.
For visual clarity, the latter two clusters are not shown in Figure~\ref{fig:age}.} We cleaned \replaced{these}{the membership lists}
following the data filtering criteria from \citet[][Appendix
B]{GaiaCollaboration2018}, except that we weakened the parallax
precision requirement to $\varpi/\sigma_\varpi>5$.  \added{This also involved cuts
on the photometric signal to noise ratio, the number of visibility
periods used, the astrometric $\chi^2$ of the single-source solution, and the
$G_{\rm BP}-G_{\rm RP}$ color excess factor.} These filters were
designed to include genuine binaries while omitting instrumental
artifacts.

@@

Of the \noriginal\ candidate \cn\ members reported by
\citet{KounkelCovey2019}, \nwithtess\ stars were amenable to rotation
period measurements ($G<17$ and $\bpmrpo>0.5$) using the TESS full
frame image data.\added{ As a matter of
scope, we restricted our attention to the \nkinwithtess\ stars
discussed in Section~\ref{sec:kinematicselection} in the spatial and
kinematic proximity of Kepler\,1627.} We extracted light curves from
the TESS images using the nearest pixel to each star, and regressed
them against systematics with the causal pixel model implemented in
the \texttt{unpopular} package \citep{hattorio_2021_cpm}.  We then
measured candidate rotation periods using a Lomb-Scargle periodogram
\citep{lomb_1976,scargle_studies_1982,astropy_2018}.  To enable cuts
on crowding, we queried the Gaia source catalog for stars within a
$21\farcs0$ radius of the target star (a radius of 1 TESS pixel).
Within this radius, we recorded the number of stars with greater
brightness than the target star, and with brightness within 1.25 TESS magnitudes of the target star.

@@

We therefore isolated each of the 144 observed transits to within
$\pm4.5$\,hr of each transit, and fitted each window with both {\it
i)} a local \added{second or fourth-order }polynomial baseline plus the transit, and {\it ii)} a local linear
trend\added{ plus the transit}.  \deleted{We considered the results both for a second and fourth-order
time-dependence in the local baseline.  }We let the mid-time of each
transit float, and then calculated the residual between the measured
mid-time and that of a periodic orbit.  This residual, the transit
timing variation, is plotted in Figure~\ref{fig:corr} against
the local linear slope for the fourth-order polynomial baseline.  The
slope of $-21 \pm 10\,{\rm min\,day}^{-1}$ is similar to that
found by \citet{holczer_time_2015}. \added{The
best-fit line yields $\chi^2 = 306.1$, with $n=140$ data points.  An alternative
model of just a flat line yields $\chi^2=315.6$.  The difference in the
Bayesian information criterion between the two models is ${\rm
BIC}_{\rm flat} - {\rm BIC}_{\rm line} = 4.5$,
which corresponds to a Bayes factor of $\approx$9.4. According to the
usual \citet{kass_bayes_1995} criteria, this is ``positive'' evidence
for the model with a finite slope.  We view it as suggestive
at best, particularly given the poor reduced $\chi^2$.}

@@

In the context of the transiting planet population, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages include K2-33
\citep{Mann_K2_33b_2016,David_et_al_2017}, DS~Tuc
\citep{benatti_possibly_2019,newton_tess_2019}, HIP~67522
\citep{rizzuto_tess_2020}, TOI~837 \citep{bouma_cluster_2020}, the
two-planet AU~Mic \citep{plavchan_planet_2020,martioli_aumicbc_2021}
and the four-planet V1298~Tau \citep{david_four_2019}.  \pn\ is one of
the smaller planets in this sample ($3.82\pm0.16\,R_\oplus$), which
could be linked to the selection effects imposed by spot-induced
photometric variability at very young ages \citep[{\it
e.g.},][]{zhou_2021_tois}.  \replaced{However,}{However, it seems that} smaller planets could have been
detected: \added{based on the per-target detection contours, }the Kepler pipeline's median completeness extended to
$1.6\,R_\oplus$ at 10~day orbital periods, and $3.3\,R_\oplus$ at
100~days
\citep{2021ascl.soft07027B}.
\added{These limits account for the spot-induced variability in the
system through
a correction based on the Combined Differential Photometric Precision
in the \sn\ light curve over the relevant transit timescales
\citep{2017ksci.rept...19B}.} The large size of \pn\ relative
to most Kepler mini-Neptunes might therefore support a picture
in which the typical $5\,M_\oplus$\deleted{ to 10$\,M_\oplus$} mini-Neptune
\citep{wu_mass_2019} loses a significant fraction of its primordial
atmosphere over its first gigayear
\citep{Owen_Wu_2013,ginzburg_corepowered_2018}.  
\added{
It could also be consistent with a scenario in which an earlier ``boil-off'' of
the planet's atmosphere during disk dispersal decreases the entropy of
the planetary interior, leading to a $\sim$10$^8$ year Kelvin-Helmholtz
contraction timescale
\citep{owen_constraining_2020}.
Confirming either of these scenarios would require a measurement
of the planetary mass; otherwise, alternative explanations for its large size
could include that it is abnormally massive, or that it has an abnormally
large envelope to core mass ratio.}
